Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-21 qhtv2.tex
Clarifications section 4

\section{Optimising queuing filters}
\label{sec:optimising}

The parameter $L$ determines how many subfilters appear in the queuing construction. Summing up the false positive and false negative rates, we have a total error rate 
\begin{equation}
	\operatorname{ER}_{\mathcal Q, cn}^{w}
	= 1 - \alpha \beta^{L-1} + \alpha' \beta'^{L-1}
\end{equation}
where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ only depend on $c$ and the choice of subfilter type $\mathcal F$. Differentiating with respect to $L$ and equating to zero gives an optimum
\begin{equation*}
	L = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
\end{equation*}

>>>>

\section{Optimising queuing filters}
\label{sec:optimising}
Let us relax, temporarily, the a priori constraint that $w = cL$. The parameter $L$ determines how many subfilters appear in the queuing construction. Summing up the false positive and false negative rates, we have a total error rate 
\begin{equation}
	\operatorname{ER}_{\mathcal Q, cn}^{w}
	= 1 - \alpha \beta^{L-1} + \alpha' \beta'^{L-1}
\end{equation}
where $\beta = 1 - \FP_{\mathcal F, c}$, $\beta' = u_c$, 
$\alpha = \frac1c \sum_{\ell = 0}^{c-1}1 - \FP_{\mathcal F, \ell}$ and $\alpha' = \frac1c \sum_{\ell = 0}^{c-1} u_\ell$ only depend on $c$ and the choice of subfilter type $\mathcal F$. Differentiating with respect to $L$ and equating to zero gives an optimum
\begin{equation*}
	L_{c, \mathcal F} = -\log((\alpha \beta' \log(\beta))/(\alpha'\beta \log(\beta')))/\log(\beta/\beta').
\end{equation*} 
Thus for a given $c$ and choice of subfilter $\mathcal F$ we get an optimal value of $L = L_{c, \mathcal F}$,
and we set, \emph{a posteriori}, $w \gets cL$.

If instead $w$ is a given value, solving $w = c L_{c, \mathcal F}$ analytically may be challenging.
A practical solution is to interpolate between explicitly computed values $cL_{c, \mathcal F}$ to find the 
closest match for the target $w$.
